Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-13 tex/VHzQ.tex
Added more details to NIR variability results

Using the extended datasets described in Section~\ref{sec:NIR_data},
we select objects with at least 8 measurements observed with intervals
of at least 30 days, in at least one filter. The the average
calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
aperJky3/aperJky3Err}$\geq$8). The clipped median and median absolute
deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deviation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points.  With these
criteria, there are 21 WFCAM and 12 VISTA objects with 1 object (VIK
J1148+0056) in common to both, and this sample of 32 is our starting
point for variability investigations.

>>>>

Using the extended datasets described in Section~\ref{sec:NIR_data},
we select objects with at least 8 measurements observed with intervals
of at least 30 days, in at least one filter. The the average
calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
with the signal-to-noise is required to be $\geq8$ (i.e. {\tt
aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 21 WFCAM 
and 12 VISTA objects with 1 object (VIK J1148+0056) in common to both, 
and this sample of 32 is our starting
point for variability investigations.

The clipped median and median absolute deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deviation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points. We apply the criteria 
$var>=3.$ to light-curves from the original measurements and also to light-curves 
where measurements have been averaged over different time-scales to improve 
the signal-to-noise. We found that two quasars showed signs of variability:
MMT J0215-0529 in the Y-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
SDSS J0959+0227 in the Y and H bands, with timescales of 1 year or 6 months 
for Y only. The H-band amplitude was 0.9 mag and the Y-band amplitude was 1.2 mag if averaged over 6 months,
or 0.9 mag if averaged over 1 year.
